A linearization procedure for constrained multibody systems

### 2012-08-24 PetersonGedeHubbard2012.tex
Added example's equations

\documentclass[smallcondensed]{svjour3}                     % onecolumn (standard format)
\RequirePackage{fix-cm}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{pgf}
%\usepackage[polutonikogreek]{babel}

@@

\begin{figure}
  \centering
  \input{rollingdisc.pgf}
  \caption{Rolling disc configuration}
  \label{fig:disc}
\end{figure}
\section{Derivation of linearization algorithm}
\label{sec:derivations}

>>>>

\documentclass[smallcondensed]{svjour3}                     % onecolumn (standard format)
%\documentclass{article}
\RequirePackage{fix-cm}

\usepackage{graphicx}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{pgf}
%\usepackage[polutonikogreek]{babel}

@@

\begin{figure}
  \centering
  \input{rollingdisc.pgf}
  \caption{Rolling disc configuration}
  \label{fig:disc}
\end{figure}

The matrices which make up the linear equations were created using the method
presented in Section \ref{sec:results}. It is very important to note that the
quantities in the matrices represent the states at the point of linearization.
This leads to $q$'s, $u$'s, $\dot{q}$'s, and $\dot{u}$'s all showing up. The
nonlinear equations need to be evaluated at a point to determine all of these
quantities. The $\dot{u}$ quantities are not actually required to be 0, so
equilibrium is not a requirement of the linearization point chosen.

The independent state vector is:
\begin{align}
\begin{bmatrix}
\delta \bm{q}_i \\
\delta \bm{u}_i
\end{bmatrix} =
\begin{bmatrix}
q_0 &
q_1 &
q_2 &
q_3 &
q_4 &
u_0 &
u_1 &
u_2
\end{bmatrix}^T
\end{align}

And the complete state vector is:
\begin{align}
\begin{bmatrix}
\delta \bm{q} \\
\delta \bm{u}
\end{bmatrix} =
\left[
\begin{array}{cccccccccccc}
q_0 &
q_1 &
q_2 &
q_3 &
q_4 &
q_5 &
u_0 &
u_1 &
u_2 &
u_3 &
u_4 &
u_5
\end{array}
\right]^T
\end{align}

The matrices which make up the linear equations have been partitioned for
readability.

\begin{equation}
\begin{aligned}
  \left[
    \begin{array}{cc}
      \tilde{M}_{qq} & \bm{0}_{n \times o} \\
      \tilde{M}_{uqc} & \tilde{M}_{uuc} \\
      \tilde{M}_{uqd} & \tilde{M}_{uud}
    \end{array}
    \right]=\\
\end{aligned}
\end{equation}
\begin{equation*}
\begin{aligned}
\left[\begin{smallmatrix}- c_{1} s_{2} & c_{2} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\s_{1} & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\c_{1} c_{2} & s_{2} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & c_{0} c_{2} - s_{0} s_{1} s_{2} & c_{0} s_{1} s_{2} + c_{2} s_{0} & - c_{1} s_{2} & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & - c_{1} s_{0} & c_{0} c_{1} & s_{1} & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & c_{0} s_{2} + c_{2} s_{0} s_{1} & - c_{0} c_{2} s_{1} + s_{0} s_{2} & c_{1} c_{2} & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & - r s_{2} u_{1} & 0 & 0 & 0 & 0 & c_{2} r & 0 & 1 & 0 & 0\\0 & 0 & r \left(- c_{2} u_{2} + s_{2} u_{0}\right) & 0 & 0 & 0 & - c_{2} r & 0 & - r s_{2} & 0 & 1 & 0\\0 & 0 & c_{2} r u_{1} & 0 & 0 & 0 & 0 & r s_{2} & 0 & 0 & 0 & 1\\0 & 0 & 0 & 0 & 0 & 0 & - \frac{1}{4} m r^{2} & 0 & 0 & 0 & - c_{2} m r & 0\\0 & 0 & 0 & 0 & 0 & 0 & 0 & - \frac{1}{2} m r^{2} & 0 & c_{2} m r & 0 & m r s_{2}\\0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & - \frac{1}{4} m r^{2} & 0 & - m r s_{2} & 0\end{smallmatrix}\right]
\end{aligned}
\end{equation*}

\begin{equation}
\begin{aligned}
\left[
    \begin{array}{c}
    (\tilde{A}_{qq} + \tilde{A}_{qu} C_1 ) C_0 \\
    (\tilde{A}_{uqc} + \tilde{A}_{uuc} C_1 ) C_0\\
    (\tilde{A}_{uqd} + \tilde{A}_{uud} C_1 ) C_0
    \end{array}
\right] =\\
\end{aligned}
\end{equation}

\scriptsize
\begin{equation*}
\begin{aligned}
\left[\begin{smallmatrix}0 & - s_{1} s_{2} \dot{q}_{0} & c_{1} c_{2} \dot{q}_{0} + s_{2} \dot{q}_{1} & 0 & 0\\0 & - c_{1} \dot{q}_{0} & 0 & 0 & 0\\0 & c_{2} s_{1} \dot{q}_{0} & c_{1} s_{2} \dot{q}_{0} - c_{2} \dot{q}_{1} & 0 & 0\\\left(- c_{0} c_{2} + s_{0} s_{1} s_{2}\right) \dot{q}_{4} + \left(c_{0} s_{1} s_{2} + c_{2} s_{0}\right) \dot{q}_{3} & s_{2} \left(- c_{0} c_{1} \dot{q}_{4} + c_{1} s_{0} \dot{q}_{3} - s_{1} \dot{q}_{5}\right) & c_{1} c_{2} \dot{q}_{5} + r s_{2} u_{1} + \left(c_{0} s_{2} + c_{2} s_{0} s_{1}\right) \dot{q}_{3} + \left(- c_{0} c_{2} s_{1} + s_{0} s_{2}\right) \dot{q}_{4} & 0 & 0\\c_{1} \left(c_{0} \dot{q}_{3} + s_{0} \dot{q}_{4}\right) & c_{0} s_{1} \dot{q}_{4} - c_{1} \dot{q}_{5} - s_{0} s_{1} \dot{q}_{3} & r \left(c_{2} u_{2} - s_{2} u_{0}\right) & 0 & 0\\- \left(c_{0} s_{2} + c_{2} s_{0} s_{1}\right) \dot{q}_{4} + \left(- c_{0} c_{2} s_{1} + s_{0} s_{2}\right) \dot{q}_{3} & c_{2} \left(c_{0} c_{1} \dot{q}_{4} - c_{1} s_{0} \dot{q}_{3} + s_{1} \dot{q}_{5}\right) & c_{1} s_{2} \dot{q}_{5} - c_{2} r u_{1} + \left(- c_{0} c_{2} + s_{0} s_{1} s_{2}\right) \dot{q}_{3} - \left(c_{0} s_{1} s_{2} + c_{2} s_{0}\right) \dot{q}_{4} & 0 & 0\\0 & 0 & c_{2} r u_{1} \dot{q}_{2} & 0 & 0\\0 & 0 & r \left(- c_{2} u_{0} - s_{2} u_{2}\right) \dot{q}_{2} & 0 & 0\\0 & 0 & r s_{2} u_{1} \dot{q}_{2} & 0 & 0\\0 & - c_{1} c_{2} g m r & m r \left(c_{2}^{2} r u_{0} u_{1} + c_{2} r s_{2} u_{1} u_{2} + g s_{1} s_{2} + s_{2} u_{0} u_{5} - s_{2} u_{2} u_{3} - s_{2} \dot{u}_{4}\right) & 0 & 0\\0 & 0 & m r \left(c_{2}^{2} r u_{2} - 2 c_{2} r s_{2} u_{0} u_{2} - c_{2} u_{0} u_{4} + c_{2} u_{1} u_{3} - c_{2} \dot{u}_{5} + r s_{2}^{2} u_{0} + r u_{1} + s_{2} u_{1} u_{5} - s_{2} u_{2} u_{4} + s_{2} \dot{u}_{3}\right) & 0 & 0\\0 & - c_{1} g m r s_{2} & m r \left(- c_{2} g s_{1} + c_{2} r s_{2} u_{0} u_{1} - c_{2} u_{0} u_{5} + c_{2} u_{2} u_{3} + c_{2} \dot{u}_{4} + r s_{2}^{2} u_{1} u_{2}\right) & 0 & 0\end{smallmatrix}\right]
\end{aligned}
\end{equation*}

\normalsize

\begin{equation}
\begin{aligned}
\left[
\begin{array}{c}
\tilde{A}_{qu} C_2 \\
\tilde{A}_{uuc} C_2 \\
\tilde{A}_{uud} C_2 \\
    \end{array}
\right] =\\
\end{aligned}
\end{equation}
\begin{equation*}
\begin{aligned}
\left[\begin{smallmatrix}1 & 0 & 0\\0 & 1 & 0\\0 & 0 & 1\\0 & - c_{2} r & 0\\c_{2} r & 0 & r s_{2}\\0 & - r s_{2} & 0\\0 & r s_{2} \dot{q}_{2} & 0\\- r s_{2} \dot{q}_{2} & 0 & c_{2} r \dot{q}_{2}\\0 & - c_{2} r \dot{q}_{2} & 0\\- c_{2} m r u_{5} & \frac{1}{4} m r^{2} \left(4 c_{2} s_{2} u_{0} + 4 s_{2}^{2} u_{2} - 5 u_{2}\right) & \frac{1}{4} m r \left(4 c_{2} u_{3} - r u_{1}\right)\\m r \left(c_{2}^{2} r u_{2} - c_{2} r s_{2} u_{0} - s_{2} u_{4}\right) & m r \left(- c_{2} u_{5} + s_{2} u_{3}\right) & m r \left(c_{2} r s_{2} u_{2} + c_{2} u_{4} - r s_{2}^{2} u_{0}\right)\\\frac{1}{4} m r \left(r u_{1} - 4 s_{2} u_{5}\right) & \frac{1}{4} m r^{2} \left(- 4 c_{2} s_{2} u_{2} + 4 s_{2}^{2} u_{0} + u_{0}\right) & m r s_{2} u_{3}\end{smallmatrix}\right]
\end{aligned}
\end{equation*}

\section{Derivation of linearization algorithm}
\label{sec:derivations}
